The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-27 paper.tex
Following discussion with Claire and Julia, commenting out section 2 on the experimental studies
Kept some of the diagrams for the introduction

To support the reflection, it may be useful to consider a few experimental
results. We observed anthropomorphism in several short- and long-term human-robot
interaction studies that we carried out with embodied robots, both in
ecologically valid real-world environments and controlled lab settings. Those
experiments are presented in details in section~\ref{sec:overview-studies}. We
only highlight here some qualitative results in order to trigger some initial
thoughts.

Figures~\ref{fig:roomba-activities} and~\ref{fig:roomba-perception} (on
page~\pageref{fig:roomba-perception}) give a first perspective on how naive
users interact and perceive robots over a long period of time. Here,
\emph{Roomba} vacuum cleaning robots were given to nine households for a
6-months period. The aim was to explore how people use and perceive the robot
over time, and how they generally live with the Roomba in their home. At various
time points, users were asked to rate their perception of different features of
the robot on a 7-point rating scale. As Figure~\ref{fig:roomba-perception}
shows, some features remained stable over time (\emph{ease of use} and
\emph{fun}), and others decreased: the perceived \emph{usefulness},
\emph{intelligence} and \emph{impact} on their household.  \emph{intelligence}
and \emph{impact} reflect the cognitive engagement of the user towards the
machine: we can assume that one does not care to engage in a (cognitive)
interaction with an artifact perceived as non-intelligent and with no impact on
his/her life (and the level of activity pictured on
Figure~\ref{fig:roomba-activities} qualitatively confirms this intuition). Even
if one can argue that the Roomba is not designed to foster interaction, it
raises a first question: how to sustain engagement between a robot and a human
over a long period of time? And, as a pre-requisite to answer, do we actually
understand the psychological phenomenon, and can we effectively account for the
dynamics of these interactions?

@@

Figure~\ref{fig:qualitative-score} (page~\pageref{fig:qualitative-score}) calls
for other initial remarks. This diagram comes from a study where 13 pairs of
children (4-5 years old) played for about 20 minutes a Domino game with a robot
(the robot was tasked to carry domino pieces from one child to the other). The
$x$-axis represents the number of social interactions between the children and
the robot (like talking or showing objects), based on video annotations. On the
$y$-axis, we have a synthetic qualitative measurement of anthropomorphic
projections based on two questionnaires. The correlation between both these
values is significantly \emph{negative}: the more the children engaged into
interaction, the less prone to anthropomorphic projections they were. This
diagram also highlights an interesting cluster of children who did not interact
much with the robot, and still reported a strong anthropomorphic perception of
the robot.

@@

Based on an extensive literature review~\citep{fink_anthropomorphism_2012},
several field and lab studies~\citep{ fink_anthropomorphic_2012,
fink_living_2013, fink2014which, lemaignan2014dynamics} and insights from the
cognitive neurosciences, we propose to discuss anthropomorphism from three
complementary perspectives.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		OVERVIEW ON OUR STUDIES
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Studying anthropomorphism in HRI}
\label{sec:overview-studies}

In this section we give a brief overview of the studies that we conducted to
investigate anthropomorphism in human-robot interaction. Note that it was not
the main purpose of these studies to analyze in detail the effect of different
dimensions human-likeness of a robot on the user's perception of and interaction
with the robot. Each of these studies were motivated also by other research
questions, and we encourage the reader to refer to our other main publications
about these studies for more details.

\subsection{Roomba study: how people live with a vacuum cleaning robot}

We openly explored long-term interactions between human users and a domestic
service robot in a 6-months lasting ethnographic study~\citep{fink_living_2013}. 
We gave a commercially
available vacuum cleaning robot (iRobot's Roomba, see Figure
\ref{fig:aibo-roomba-ipad} middle) to nine households. 
%in the French speaking
%part of Switzerland. 
%The fairly diverse sample of households consisted of 2
%single homes, 1 couple, and 6 families with children in their home. In total,
%this summed up to 30 participants: 15 adults (26-71 years old, mean age 43.6
%years), and 15 children (6 months to 18 years old). During the 6 months, each
%household was visited 5 times to conduct interviews and make field observations
%in the households. Moreover, during several weeks, households were asked to fill
%in a diary to report the usage of the robot and other cleaning activities.
Hereafter, we refer to this study as the ``Roomba study''. It is one of very few 
long-term human-robot interaction studies in the domestic environment. 
In the following, we present findings in respect of two aspects: First, we
qualitatively describe what kinds of anthropomorphic interactions between
participants and the robot were observed and outline how these interactions
evolved over time.  Second, we present people's perception of human-likeness and
social capabilities of the robot and how this perception changed over
time.

%\footnote{\hl{note that these two different kinds of data
%(behavior/interaction and perception) already show that we try to measure
%anthropomorphism from these two angles!}}

%The main goal of this study was to explore how households live with a vacuum
%cleaning robot over an extended period of time. We wanted to analyze how the
%usage of and interaction with the robot evolve over time, and to identify
%adoption phases as well as factors that impact on the long-term acceptance of
%service robots in homes.

\subsubsection{Anthropomorphic interactions with the robot\\}

It has been described in several previous studies of the Roomba that users tend
to engage in a variety of non-cleaning activities associated with the robot,
including, but not limited to, naming, ascribing personality and gender
\citep{forlizzi_service_2006,forlizzi_how_2007,krumm_my_2007,sung_domestic_2010}.
\cite{sung_housewives_2008} carried out a survey among 379 Roomba users to
investigate how common these activities are. The authors concluded that overall,
respondents had relatively low rates of treating Roomba as a living entity.  
Similarly, in our long-term study of the Roomba in homes, we found that only few 
people tended to interact in an anthropomorphic or human-social way with their 
vacuum cleaning robot and that this effect did not sustain. Overall, our data 
suggest that the anthropomorphic effect and the social
impact of a functional robot on a household are rather marginal.
%There were just few instances of people anthropomorphizing the robot and
%interacting with it in a human-social way. More importantly, overall, these
%anthropomorphic interactions with the robot did not last but seemed to be
%somehow related to the novelty of the robot.

We categorized several interactions and actions with the robot as
anthropomorphic or human-social (in a broader sense). 
%Examples of what we categorized as somehow social and anthropomorphic
%(human-like) interactions with the robot include \textit{watching} the robot
%for fun, giving a \textit{demo} of the robot to guests / visitors, taking a
%\textit{photo/video} of the robot, \textit{personalizing} the robot, giving a
%\textit{name} to the robot, \textit{talking} to the robot using direct speech,
%\textit{playing} with the robot, and making \textit{adjustments} to the home
%due to the robot. 
Figure \ref{fig:roomba-activities} shows how many of the 9 households engaged
in these activities during the 6 months when the study was conducted.

%\begin{figure}
%    \centering
%    \includegraphics[width=0.5\columnwidth]{roomba-activities.png}
%    \caption{Activities with the robot over time, n = 9 households. This bar
%        chart shows how many of the 9 households carried out different kinds of
%        anthropomorphic / social activities with and related to the robot at 3
%        time points during 6 months. Activities include \texttt{watching} the
%        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
%        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
%        \texttt{talking} to the robot, \texttt{playing} with the robot.
%        Participants were asked to report on these activities at 3 time points
%        after the robot was deployed in their home: after 2 weeks, after 2 months,
%        and after 6 months.} 
%
%\label{fig:roomba-activities}
%\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}[b]{0.48\columnwidth}
                \includegraphics[width=\textwidth]{roomba-activities.png}
                \caption{Roomba activities}
                \label{fig:roomba-activities}
        \end{subfigure}%
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.48\columnwidth}
                \includegraphics[width=\textwidth]{roomba-perception.pdf}
                \caption{Roomba perception}
                \label{fig:roomba-perception}
        \end{subfigure}
        \caption{\textbf{The Roomba study: Long-term interaction with a robot.\\}
    \textbf{a)} Activities with the robot over time, n = 9 households. This bar
        chart shows how many of the 9 households carried out different kinds of
        anthropomorphic / social activities with and related to the robot at 3
        time points during 6 months. Activities include \texttt{watching} the
        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
        \texttt{talking} to the robot, \texttt{playing} with the robot.
        Participants were asked to report on these activities at 3 time points
        after the robot was deployed in their home: after 2 weeks, after 2 months,
        and after 6 months.\\
	\textbf{b)} People's perception of the robot over time, n = 15 participants.
    		This line chart shows how people's perception of the robot evolves over
    		time. At 5 time points people were asked to rate the robot according to the
    		following aspects: the perceived \texttt{intelligence} of the robot, the
    		perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much
    		\texttt{fun} it was to use the robot, how far they found the robot had an
    		\texttt{impact} on their household, and their {overall} impression of it.}
    		\label{fig:roomba-study}
\end{figure}

\paragraph*{Watching the robot for fun.} We categorize watching a robot for fun
as an entertaining, emotional activity, reflecting a feeling of empathy for the
robot. In \cite{sung_housewives_2008} survey, 73~\% of the participants reported
to watch their Roomba running for fun. While in the beginning of our study, also
a quite high proportion (6 of 9 households) reported to watch the robot for fun,
after 2 and 6 months the number of households that engaged in this activity
decreased by half.

\paragraph*{Giving a robot demo to visitors.} It is somehow natural that owners
of innovative devices show the device to others and ask for their opinion about
it \citep{rogers_diffusion_1995}. However, this activity suggests that the robot
is presented as a new part of the household to visitors.
\cite{sung_domestic_2010} described that a vacuum cleaning robot can serve as a
mediator and encourage social interaction among people. We categorize giving a
demo of the robot to visitors / guests as such an activity. During the first 2
weeks with the robot 8 of 9 households in our study showed their robot to
others, and still after 2 and 6 months 5 of the households engaged in this
activity. This number is more or less in accordance with the 57~\% of survey
respondents who stated to give demonstrations to others
\citep{sung_housewives_2008}.

%\paragraph*{Taking photos / videos of the robot.} How far taking a photo or
%video of a robot can be seen as an anthropomorphic interaction is questionable.
%However, it reflects the fact that the robot is observed by the user who for
%some reason is motivated to record the event. The number of households that
%took a photo or video of the robot decreased over time from 5 households in the
%beginning to 1 household after 6 months.

\paragraph*{Personalizing the robot.} It has been found that people are
motivated to personalize technology as a form of self-expression (identity
projection) or when they use a technology a lot and know how to customize it
(technical identity projection) \citep{blom_personalization:_2000}. Though
\cite{sung_pimp_2009} found that some Roomba users who were given a
customization toolkit personalized their Roomba, none of the users in her study
who was \textit{not} given this toolkit personalized their Roomba. Also in our
study none of the 9 households engaged in a personalization activity.

\paragraph*{Giving a name to the robot.} Giving a name to an artificial agent
reflects a certain kind of personal relationship to the agent. By naming a
robot, it is not anonymous anymore, and might be perceived as a moral agent. As
such, naming an artificial agent can be classified as anthropomorphizing this
agent. It further suggests that the agent is talked to directly. Though more
than 23~\% of the survey participants in \cite{sung_housewives_2008} study
reported to name their Roomba, only 1 of 9 households in our study did so.

\paragraph*{Talking directly to the robot.} Using direct speech toward an object
or artificial agent that does not have the ability to recognize and process
speech (such as verbal comments) or other sound cues, is an interesting
phenomenon which can be classified as an anthropomorphic interaction. Whereas
only 11~\% of the survey respondents in \cite{sung_housewives_2008} study
reported to talk to their robot, around half of the households engaged in this
activity and the proportion did not notably decrease over time.

\paragraph*{Playing with the robot.} In our study, it were mostly children who
engaged in playing with the robot, however, most of them stopped doing so after
some time. The number of household playing with their Roomba decreased from 8
when asked after 2 weeks with the robot, to 4 households after 2 months, and 1
household after 6 months. In \cite{sung_housewives_2008} survey, 37~\% of the
Roomba owners reported to play and experiment with their robot.\\

%\paragraph*{Making adjustments to the home due to the robot.} To help Roomba
%clean, \cite{sung_housewives_2008} found in an online survey that about half of
%the 379 participants made physical modifications to their homes. This process
%is referred to as \textit{roombarization}, and it seems to be a unique aspect
%of adopting a domestic service robot. In our study, almost all the households
%made adjustments when they used the robot for the first time in front of us.
%However, during the first two weeks with the robot, only 3 households reported
%to have adjusted something due to the robot, and after 6 months it was only 1
%household that still engaged in this activity. This decrease is, however,
%logical since after some time most people had done all the necessary
%adjustments to enable the robot show a good performance.

%\paragraph*{Emerging anthropomorphic interactions.} Another, from our side more
%unexpected interaction that we would describe as somehow anthropomorphic, is
%what we call \textit{``collaborative cleaning''} with the robot. In the initial
%phase of the study, some people spontaneously helped the robot to clean by
%either picking up crumbs from the floor themselves or pushing it right in front
%of the robot. Another way of collaborating with the robot we observed was to
%help it go everywhere by spontaneously putting up the trash bin or the carpet
%in the bathroom (things that are not just lying around and need to be cleaned
%up). However, the activity of collaborative cleaning faded out soon, and we
%suspect it was encouraged by the novelty of the robot.\\

Overall, Figure \ref{fig:roomba-activities} shows that as time goes by, less
households engage in the before-mentioned non-cleaning activities with the
vacuum cleaning robot: after 2 weeks, on average, 4.67 of 9 households engage in
a human-like activity with the robot; after 2 months, the value decreases to
2.83, and after 6 months to 2.3. Our interpretation is that the nature of
human-robot interaction changes over time. More concretely, we suspect  that
anthropomorphic / human-social interactions with the robot become less over
time, and that only with some people these interactions sustain.

\subsubsection{Perception of anthropomorphic characteristics of the robot\\}

We also studied people's perception of the robot, and how it evolved over time
(see Figure \ref{fig:roomba-perception}). The main idea was to find out which of
the perceived attributes could be related to how far the robot was integrated in
the household as a cleaning tool. Concerning anthropomorphism, we included
\textit{perceived intelligence} and experienced \textit{fun} when using the
robot as indicators for the perception of human-likeness in the robot.\fixme{JF: Severin, you also mentioned impact as one factor. Please include it here below as another paragraph.}

%\begin{figure}
%    \centering
%    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}

>>>>

To support the reflection, it may be useful to consider a few experimental
results. We studied anthropomorphism effects in several short- and long-term
human-robot interaction studies that we carried out with embodied robots, both
in ecologically valid real-world environments and controlled lab settings. Those
experiments are presented in details in previously published
articles~\citep{fink_anthropomorphic_2012, fink_living_2013, fink2014which,
lemaignan2014dynamics}. We only highlight here a few qualitative results that
underline the complexity of the phenomenon.

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.48\columnwidth}
                \includegraphics[width=\textwidth]{roomba-activities.png}
                \caption{Roomba activities}
                \label{fig:roomba-activities}
        \end{subfigure}%
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.48\columnwidth}
                \includegraphics[width=\textwidth]{roomba-perception.pdf}
                \caption{Roomba perception}
                \label{fig:roomba-perception}
        \end{subfigure}
    \caption{Usage and perception of the Roomba robot over a 6 months period.}
    \label{fig:roomba}
\end{figure}

Figures~\ref{fig:roomba-activities} and~\ref{fig:roomba-perception} give a first
perspective on how naive users interact and perceive robots over a long period
of time. Here, \emph{Roomba} vacuum cleaning robots were given to nine
households for a 6-months period. The aim was to explore how people use and
perceive the robot over time, and how they generally live with the Roomba in
their home. At various time points, users were asked to rate their perception of
different features of the robot on a 7-point rating scale. As
Figure~\ref{fig:roomba-perception} shows, some features remained stable over
time (\emph{ease of use} and \emph{fun}), and others decreased: the perceived
\emph{usefulness}, \emph{intelligence} and \emph{impact} on their household.
\emph{intelligence} and \emph{impact} reflect the cognitive engagement of the
user towards the machine: we can assume that one does not care to engage in a
(cognitive) interaction with an artifact perceived as non-intelligent and with
no impact on his/her life (and the level of activity pictured on
Figure~\ref{fig:roomba-activities} qualitatively confirms this intuition). Even
if one can argue that the Roomba is not designed to foster interaction, it
raises a first question: how to sustain engagement between a robot and a human
over a long period of time? And, as a pre-requisite to answer, do we actually
understand the psychological phenomenon, and can we effectively account for the
dynamics of these interactions?

@@

Figure~\ref{fig:qualitative-score} calls for other initial remarks. This diagram
comes from a (yet unpublished) study where 13 pairs of children (4-5 years old)
played for about 20 minutes a Domino game with a robot (the robot was tasked to
carry domino pieces from one child to the other, Figure~\ref{fig:ranger-expe}).
The $x$-axis represents the number of social interactions between the children
and the robot (like talking or showing objects), based on video annotations. On
the $y$-axis, we have a synthetic qualitative measurement of anthropomorphic
projections based on two questionnaires. The correlation between both these
values is significantly \emph{negative}: the more the children engaged into
interaction, the less prone to anthropomorphic projections they were. This
diagram also highlights an interesting cluster of children who did not interact
much with the robot, and still reported a strong anthropomorphic perception of
the robot.

\begin{figure}[h!]
        \centering
        \begin{subfigure}[t]{0.48\columnwidth}
                \centering
                \includegraphics[width=0.6\textwidth]{ranger}
                \caption{The \emph{Ranger} Dominos experiment}
                \label{fig:ranger-expe}
        \end{subfigure}%
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[t]{0.48\columnwidth}
            \includegraphics[width=0.9\textwidth]{ranger-interactions-vs-qualitative-score}
            \caption{Qualitative level of anthropomorphic projections versus
            actual interactions with the robot}
            \label{fig:qualitative-score}
        \end{subfigure}
        \caption{Level of interaction with a semi-anthropomorphic robot is
        \emph{not} a predictor of anthropomorphic projections.}
    \label{fig:ranger}
\end{figure}

@@

Based on an extensive literature review~\citep{fink_anthropomorphism_2012},
several field and lab studies previously mentioned and insights from the
cognitive neurosciences, we propose to discuss anthropomorphism from three
complementary perspectives.

@@

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%
%%		OVERVIEW ON OUR STUDIES
%%
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\section{Studying anthropomorphism in HRI}
%\label{sec:overview-studies}
%
%In this section we give a brief overview of the studies that we conducted to
%investigate anthropomorphism in human-robot interaction. Note that it was not
%the main purpose of these studies to analyze in detail the effect of different
%dimensions human-likeness of a robot on the user's perception of and interaction
%with the robot. Each of these studies were motivated also by other research
%questions, and we encourage the reader to refer to our other main publications
%about these studies for more details.
%
%
%\subsection{Roomba study: how people live with a vacuum cleaning robot}
%
%We openly explored long-term interactions between human users and a domestic
%service robot in a 6-months lasting ethnographic study~\citep{fink_living_2013}. 
%We gave a commercially
%available vacuum cleaning robot (iRobot's Roomba, see Figure
%\ref{fig:aibo-roomba-ipad} middle) to nine households. 
%%in the French speaking
%%part of Switzerland. 
%%The fairly diverse sample of households consisted of 2
%%single homes, 1 couple, and 6 families with children in their home. In total,
%%this summed up to 30 participants: 15 adults (26-71 years old, mean age 43.6
%%years), and 15 children (6 months to 18 years old). During the 6 months, each
%%household was visited 5 times to conduct interviews and make field observations
%%in the households. Moreover, during several weeks, households were asked to fill
%%in a diary to report the usage of the robot and other cleaning activities.
%Hereafter, we refer to this study as the ``Roomba study''. It is one of very few 
%long-term human-robot interaction studies in the domestic environment. 
%In the following, we present findings in respect of two aspects: First, we
%qualitatively describe what kinds of anthropomorphic interactions between
%participants and the robot were observed and outline how these interactions
%evolved over time.  Second, we present people's perception of human-likeness and
%social capabilities of the robot and how this perception changed over
%time.
%
%%\footnote{\hl{note that these two different kinds of data
%%(behavior/interaction and perception) already show that we try to measure
%%anthropomorphism from these two angles!}}
%
%%The main goal of this study was to explore how households live with a vacuum
%%cleaning robot over an extended period of time. We wanted to analyze how the
%%usage of and interaction with the robot evolve over time, and to identify
%%adoption phases as well as factors that impact on the long-term acceptance of
%%service robots in homes.
%
%
%\subsubsection{Anthropomorphic interactions with the robot\\}
%
%It has been described in several previous studies of the Roomba that users tend
%to engage in a variety of non-cleaning activities associated with the robot,
%including, but not limited to, naming, ascribing personality and gender
%\citep{forlizzi_service_2006,forlizzi_how_2007,krumm_my_2007,sung_domestic_2010}.
%\cite{sung_housewives_2008} carried out a survey among 379 Roomba users to
%investigate how common these activities are. The authors concluded that overall,
%respondents had relatively low rates of treating Roomba as a living entity.  
%Similarly, in our long-term study of the Roomba in homes, we found that only few 
%people tended to interact in an anthropomorphic or human-social way with their 
%vacuum cleaning robot and that this effect did not sustain. Overall, our data 
%suggest that the anthropomorphic effect and the social
%impact of a functional robot on a household are rather marginal.
%%There were just few instances of people anthropomorphizing the robot and
%%interacting with it in a human-social way. More importantly, overall, these
%%anthropomorphic interactions with the robot did not last but seemed to be
%%somehow related to the novelty of the robot.
%
%We categorized several interactions and actions with the robot as
%anthropomorphic or human-social (in a broader sense). 
%%Examples of what we categorized as somehow social and anthropomorphic
%%(human-like) interactions with the robot include \textit{watching} the robot
%%for fun, giving a \textit{demo} of the robot to guests / visitors, taking a
%%\textit{photo/video} of the robot, \textit{personalizing} the robot, giving a
%%\textit{name} to the robot, \textit{talking} to the robot using direct speech,
%%\textit{playing} with the robot, and making \textit{adjustments} to the home
%%due to the robot. 
%Figure \ref{fig:roomba-activities} shows how many of the 9 households engaged
%in these activities during the 6 months when the study was conducted. 
%
%%\begin{figure}
%%    \centering
%%    \includegraphics[width=0.5\columnwidth]{roomba-activities.png}
%%    \caption{Activities with the robot over time, n = 9 households. This bar
%%        chart shows how many of the 9 households carried out different kinds of
%%        anthropomorphic / social activities with and related to the robot at 3
%%        time points during 6 months. Activities include \texttt{watching} the
%%        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
%%        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
%%        \texttt{talking} to the robot, \texttt{playing} with the robot.
%%        Participants were asked to report on these activities at 3 time points
%%        after the robot was deployed in their home: after 2 weeks, after 2 months,
%%        and after 6 months.} 
%%
%%\label{fig:roomba-activities}
%%\end{figure}
%
%\begin{figure}
%        \centering
%        \begin{subfigure}[b]{0.48\columnwidth}
%                \includegraphics[width=\textwidth]{roomba-activities.png}
%                \caption{Roomba activities}
%                \label{fig:roomba-activities}
%        \end{subfigure}%
%        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
%          %(or a blank line to force the subfigure onto a new line)
%        \begin{subfigure}[b]{0.48\columnwidth}
%                \includegraphics[width=\textwidth]{roomba-perception.pdf}
%                \caption{Roomba perception}
%                \label{fig:roomba-perception}
%        \end{subfigure}
%        \caption{\textbf{The Roomba study: Long-term interaction with a robot.\\}
%    \textbf{a)} Activities with the robot over time, n = 9 households. This bar
%        chart shows how many of the 9 households carried out different kinds of
%        anthropomorphic / social activities with and related to the robot at 3
%        time points during 6 months. Activities include \texttt{watching} the
%        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
%        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
%        \texttt{talking} to the robot, \texttt{playing} with the robot.
%        Participants were asked to report on these activities at 3 time points
%        after the robot was deployed in their home: after 2 weeks, after 2 months,
%        and after 6 months.\\
%	\textbf{b)} People's perception of the robot over time, n = 15 participants.
%    		This line chart shows how people's perception of the robot evolves over
%    		time. At 5 time points people were asked to rate the robot according to the
%    		following aspects: the perceived \texttt{intelligence} of the robot, the
%    		perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much
%    		\texttt{fun} it was to use the robot, how far they found the robot had an
%    		\texttt{impact} on their household, and their {overall} impression of it.}
%    		\label{fig:roomba-study}
%\end{figure}
%
%
%\paragraph*{Watching the robot for fun.} We categorize watching a robot for fun
%as an entertaining, emotional activity, reflecting a feeling of empathy for the
%robot. In \cite{sung_housewives_2008} survey, 73~\% of the participants reported
%to watch their Roomba running for fun. While in the beginning of our study, also
%a quite high proportion (6 of 9 households) reported to watch the robot for fun,
%after 2 and 6 months the number of households that engaged in this activity
%decreased by half. 
%
%\paragraph*{Giving a robot demo to visitors.} It is somehow natural that owners
%of innovative devices show the device to others and ask for their opinion about
%it \citep{rogers_diffusion_1995}. However, this activity suggests that the robot
%is presented as a new part of the household to visitors.
%\cite{sung_domestic_2010} described that a vacuum cleaning robot can serve as a
%mediator and encourage social interaction among people. We categorize giving a
%demo of the robot to visitors / guests as such an activity. During the first 2
%weeks with the robot 8 of 9 households in our study showed their robot to
%others, and still after 2 and 6 months 5 of the households engaged in this
%activity. This number is more or less in accordance with the 57~\% of survey
%respondents who stated to give demonstrations to others
%\citep{sung_housewives_2008}.
%
%%\paragraph*{Taking photos / videos of the robot.} How far taking a photo or
%%video of a robot can be seen as an anthropomorphic interaction is questionable.
%%However, it reflects the fact that the robot is observed by the user who for
%%some reason is motivated to record the event. The number of households that
%%took a photo or video of the robot decreased over time from 5 households in the
%%beginning to 1 household after 6 months.
%
%\paragraph*{Personalizing the robot.} It has been found that people are
%motivated to personalize technology as a form of self-expression (identity
%projection) or when they use a technology a lot and know how to customize it
%(technical identity projection) \citep{blom_personalization:_2000}. Though
%\cite{sung_pimp_2009} found that some Roomba users who were given a
%customization toolkit personalized their Roomba, none of the users in her study
%who was \textit{not} given this toolkit personalized their Roomba. Also in our
%study none of the 9 households engaged in a personalization activity.
%
%\paragraph*{Giving a name to the robot.} Giving a name to an artificial agent
%reflects a certain kind of personal relationship to the agent. By naming a
%robot, it is not anonymous anymore, and might be perceived as a moral agent. As
%such, naming an artificial agent can be classified as anthropomorphizing this
%agent. It further suggests that the agent is talked to directly. Though more
%than 23~\% of the survey participants in \cite{sung_housewives_2008} study
%reported to name their Roomba, only 1 of 9 households in our study did so. 
%
%\paragraph*{Talking directly to the robot.} Using direct speech toward an object
%or artificial agent that does not have the ability to recognize and process
%speech (such as verbal comments) or other sound cues, is an interesting
%phenomenon which can be classified as an anthropomorphic interaction. Whereas
%only 11~\% of the survey respondents in \cite{sung_housewives_2008} study
%reported to talk to their robot, around half of the households engaged in this
%activity and the proportion did not notably decrease over time. 
%
%\paragraph*{Playing with the robot.} In our study, it were mostly children who
%engaged in playing with the robot, however, most of them stopped doing so after
%some time. The number of household playing with their Roomba decreased from 8
%when asked after 2 weeks with the robot, to 4 households after 2 months, and 1
%household after 6 months. In \cite{sung_housewives_2008} survey, 37~\% of the
%Roomba owners reported to play and experiment with their robot.\\ 
%
%%\paragraph*{Making adjustments to the home due to the robot.} To help Roomba
%%clean, \cite{sung_housewives_2008} found in an online survey that about half of
%%the 379 participants made physical modifications to their homes. This process
%%is referred to as \textit{roombarization}, and it seems to be a unique aspect
%%of adopting a domestic service robot. In our study, almost all the households
%%made adjustments when they used the robot for the first time in front of us.
%%However, during the first two weeks with the robot, only 3 households reported
%%to have adjusted something due to the robot, and after 6 months it was only 1
%%household that still engaged in this activity. This decrease is, however,
%%logical since after some time most people had done all the necessary
%%adjustments to enable the robot show a good performance.
%
%%\paragraph*{Emerging anthropomorphic interactions.} Another, from our side more
%%unexpected interaction that we would describe as somehow anthropomorphic, is
%%what we call \textit{``collaborative cleaning''} with the robot. In the initial
%%phase of the study, some people spontaneously helped the robot to clean by
%%either picking up crumbs from the floor themselves or pushing it right in front
%%of the robot. Another way of collaborating with the robot we observed was to
%%help it go everywhere by spontaneously putting up the trash bin or the carpet
%%in the bathroom (things that are not just lying around and need to be cleaned
%%up). However, the activity of collaborative cleaning faded out soon, and we
%%suspect it was encouraged by the novelty of the robot.\\
%
%Overall, Figure \ref{fig:roomba-activities} shows that as time goes by, less
%households engage in the before-mentioned non-cleaning activities with the
%vacuum cleaning robot: after 2 weeks, on average, 4.67 of 9 households engage in
%a human-like activity with the robot; after 2 months, the value decreases to
%2.83, and after 6 months to 2.3. Our interpretation is that the nature of
%human-robot interaction changes over time. More concretely, we suspect  that
%anthropomorphic / human-social interactions with the robot become less over
%time, and that only with some people these interactions sustain.
%
%
%\subsubsection{Perception of anthropomorphic characteristics of the robot\\}
%
%We also studied people's perception of the robot, and how it evolved over time
%(see Figure \ref{fig:roomba-perception}). The main idea was to find out which of
%the perceived attributes could be related to how far the robot was integrated in
%the household as a cleaning tool. Concerning anthropomorphism, we included
%\textit{perceived intelligence} and experienced \textit{fun} when using the
%robot as indicators for the perception of human-likeness in the robot.\fixme{JF: Severin, you also mentioned impact as one factor. Please include it here below as another paragraph.}
%
%%\begin{figure}
%%    \centering
%%    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}
%
%%    \begin{tikzpicture}[scale=0.5, y = 2cm]
%%    %axis
%%    \draw (0,0) -- coordinate (x axis mid) (20,0);
%%    \draw (0,0) -- coordinate (y axis mid) (0,7);
%%    %ticks
%%    \foreach \x in {0,4,...,20}
%%        \draw (\x,1pt) -- (\x,-3pt);
%%    \foreach \y in {1,...,7} 
%%        \draw[black!20] (20,\y) -- (-3pt,\y);
%%    \foreach \y in {1,...,7} 
%%        \draw (-3pt, \y) node[anchor=east] {\y}; 
%%    %labels
%%    \node[below=0.8cm] at (x axis mid) {People's perception (n = 15)};
%%    \node at (2, -0.4) {\tiny expectations};
%%    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
%%    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
%%    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
%%    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
%%
%%    \draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
%%
%%    \draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
%%    \draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
%%    \draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
%%    \draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
%%    \draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
%%
%%    \draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
%%
%%    \end{tikzpicture}
%
%
%%    \caption{People's perception of the robot over time, n = 15 participants.
%%    This line chart shows how people's perception of the robot evolves over
%%    time. At 5 time points people were asked to rate the robot according to the
%%    following aspects: the perceived \texttt{intelligence} of the robot, the
%%    perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much
%%    \texttt{fun} it was to use the robot, how far they found the robot had an
%%    \texttt{impact} on their household, and their {overall} impression of it.}
%%
%%    \label{fig:roomba-perception}
%%\end{figure}
%
%\paragraph*{Perceived intelligence.} On a scale from 1-7, people were not sure
%about how intelligent they should expect the robot to be (mean value 3.9). The
%rating did not change much and not significantly over time (average ratings
%between 3.3-4.2) \citep{fink_living_2013}. Interestingly, at all five time
%points, male participants rated the robot as more intelligent (average 4.5) than
%females (average 3.4), however, this difference was not significant. When asked
%why they thought Roomba possesses intelligence, men more often referred to the
%'robot side' of Roomba: its abilities to detect and avoid obstacles, stairs, and
%being able to recharge itself. Contrary, women referred to its rather limited
%vacuuming performance and found it was not as intelligent because \textit{``it
%doesn't see where the dirt is, it sometimes leaves it, it can't be smart!''}.
%This difference in the perception of intelligence of a robot suggests that
%gender,and probably other individual characteristics need to be taken into
%account.
%
%\paragraph*{Experienced fun.} Participants rated the robot as 'somewhat fun'
%(values from 4.0-4.6). There was a qualitative gender difference (not
